---
title: "TITLE"
date: '`r Sys.Date()`'
bibliography: references.bib
link-citations: true
output:
  bookdown::pdf_document2:
    includes:
      in_header: preamble.tex
      before_body: head.tex
    fig_caption: true
    number_sections: false
    toc: false
  github_document:
    html_preview: false
csl: mbio.csl
fontsize: 12pt
geometry: margin=1.0in
---

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
schtools::set_knitr_opts()
knitr::opts_knit$set(
  base.dir = here::here(),
  # base.url = "../",
  fig.path = "figures/",
  dpi = 300
)
```

```{r deps, include=FALSE, message=FALSE}
library(here)
library(knitr)
library(schtools)
library(tidyverse)
```

## Abstract



### Importance


\newpage

## Introduction



## Results

Example of referencing a figure in the text (Figure \@ref(fig:alpha-diversity)).


## Discussion



## Materials and Methods



### Data Processing Steps



### Data and Code Availability

List all software and version numbers used and cite the corresponding papers or manuals.
mothur vX.X [@schloss_introducing_2009]

## Acknowledgements



## Author Contributions



## References

\setlength{\parindent}{-0.25in}
\setlength{\leftskip}{0.25in}
\noindent

<div id="refs"></div>

\setlength{\parindent}{0in}
\setlength{\leftskip}{0in}

\newpage

## Figures

```{r alpha-diversity, fig.cap="**Alpha diversity.** The distribution of Shannon and Inverse Simpson indices for all mice."}
include_graphics(here("figures/stability_alpha-diversity.pdf"))
```

